Something about classical M-theory

### 2021-04-02 new_paper.tex
3jacobi

\def\owen{\textcolor{magenta}{BW: }\textcolor{magenta}}
\def\gene{\textcolor{blue}{SR: }\textcolor{blue}}
\def\brian{\textcolor{red}{IS: }\textcolor{red}}

@@

\begin{dfn}
Let
\[
\mu_k \colon \PV^{2k}_X \times \cdots \times \PV^{2k}_X \to \PV^1_X 
\]
be the $(k+1)$-linear map of sheaves defined by the formula
\[
\mu_k (\gamma_1,\ldots, \gamma_k) \define \bigg[\partial \left(\Omega \vee \gamma_1\right)\cdots \partial \left(\Omega \vee \gamma_k\right)\bigg] \vee \Omega^{-1} .
\]
\end{dfn}

\begin{dfn}
\label{dfn:def}
Suppose $X$ is a Calabi--Yau manifold of dimension $2k+1$. 
Define the multinear maps of sheaves
\[
[\cdot, \ldots, \cdot]_j \colon \fg_X \times \cdots \times \fg_X \to \fg_X
\]
for $j=1,2,k,k+1$ by the formulas
\begin{itemize}
\item $[\cdot]_1 = \partial_\Omega$, the divergence operator;
\item $[\cdot,\cdot]_2 = \{\cdot,\cdot\}$, the Schouten bracket;
\item the only nonzero component of the $k$-ary bracket is
\[
[\gamma_1,\ldots, \gamma_k]_k = \mu_k(\gamma_1,\ldots, \gamma_k) \in \PV^1_X .
\]
\item there are two nonzero components of the $(k+1)$-ary bracket:
\[
[\gamma_1,\ldots, \gamma_k, \gamma_{k+1}]_{k+1} = \sum_{i_1 < \cdots < i_{k+1}} \gamma_{i_1} \wedge \mu_k(\gamma_{i_2},\ldots, \gamma_{i_{k+1}}) \in \PV^{2k+1}_X .
\]
and 
\[
[\nu, \gamma_1, \ldots, \gamma_k]_{k+1} = \nu \mu_k (\gamma_1,\ldots, \gamma_k) \in \PV^{1}_X .
\]
\end{itemize}
\end{dfn}

@@

The $(k+1)$-ary relations we must check are:
\begin{itemize}
\item[(1)] $\div [\gamma_1,\ldots, \gamma_k,\gamma_{k+1}]_{k+1} = \sum \{\gamma_{i_1}, [\gamma_{i_2},\ldots, \gamma_{i_{k+1}}]\}$. 
\item[(2)] $[\div \mu, \gamma_1, \ldots, \gamma_k]_{k+1} = \{\mu, [\gamma_1,\ldots, \gamma_k]_k\}$.
\item[(3)] $\div [\nu,\gamma_1,\ldots, \gamma_k]_{k+1} = \{\nu, [\gamma_1,\ldots, \gamma_{k}]_k\}$.
\end{itemize}
\end{proof}
\end{document}

>>>>

\def\brian{\textcolor{violet}{BW: }\textcolor{violet}}
\def\surya{\textcolor{blue}{SR: }\textcolor{blue}}
\def\ingmar{\textcolor{magenta}{IS: }\textcolor{magenta}}

@@

\begin{dfn}
Let
\[
\mu_k \colon \PV^{2k}_X \times \cdots \times \PV^{2k}_X \to \PV^1_X 
\]
be the $k$-linear map of sheaves defined by the formula
\[
\mu_k (\gamma_1,\ldots, \gamma_k) \define \bigg[\partial \left(\Omega \vee \gamma_1\right)\cdots \partial \left(\Omega \vee \gamma_k\right)\bigg] \vee \Omega^{-1} .
\]
\end{dfn}

\begin{lem}
For any $\gamma_1,\ldots, \gamma_k$, the vector field $\mu_k(\gamma_1,\ldots, \gamma_k)$ is divergence-free. 
\end{lem}

\begin{dfn}
\label{dfn:def}
Suppose $X$ is a Calabi--Yau manifold of dimension $2k+1$. 
Define the multinear maps of sheaves
\[
[\cdot, \ldots, \cdot]_j \colon \fg_X \times \cdots \times \fg_X \to \Pi^j \fg_X
\]
for $j=1,2,k,k+1$ by the formulas
\begin{itemize}
\item $[\cdot]_1 = \partial_\Omega$, the divergence operator;
\item $[\cdot,\cdot]_2 = \{\cdot,\cdot\}$, the Schouten bracket;
\item the only nonzero component of the $k$-ary bracket is
\[
[\gamma_1,\ldots, \gamma_k]_k = \mu_k(\gamma_1,\ldots, \gamma_k) \in \PV^1_X .
\]
\item there are two nonzero components of the $(k+1)$-ary bracket:
\[
[\gamma_1,\ldots, \gamma_k, \gamma_{k+1}]_{k+1} = \sum_{i_1 < \cdots < i_{k+1}} \gamma_{i_1} \wedge \mu_k(\gamma_{i_2},\ldots, \gamma_{i_{k+1}}) \in \PV^{2k+1}_X .
\]
and 
\[
[\nu, \gamma_1, \ldots, \gamma_k]_{k+1} = \# \nu \mu_k (\gamma_1,\ldots, \gamma_k) + \sum_{i=1}^k \bigg[\left(\Omega \vee \{\nu, \gamma_1\}\right)\cdots \Hat{\partial \left(\Omega \vee \gamma_k\right)} \cdots \partial \left(\Omega \vee \gamma_k\right) \bigg] \vee \Omega^{-1} \in \PV^{1}_X .
\]
\end{itemize}
\end{dfn}

@@

The $(k+1)$-ary relations we must check are:
\begin{itemize}
\item[(1)] $\div [\gamma_1,\ldots, \gamma_k,\gamma_{k+1}]_{k+1} = \sum \{\gamma_{i_1}, [\gamma_{i_2},\ldots, \gamma_{i_{k+1}}]\}$. 
\item[(2)] $[\div \mu, \gamma_1, \ldots, \gamma_k]_{k+1} = \{\mu, [\gamma_1,\ldots, \gamma_k]_k\} + \sum [\{\mu, \gamma_{i_1}\}, \gamma_{i_2}, \ldots, \gamma_{i_{k}}]_{k}$.
\item[(3)] $\div [\nu,\gamma_1,\ldots, \gamma_k]_{k+1} = \{\nu, [\gamma_1,\ldots, \gamma_{k}]_k\}$.
\end{itemize}

\ul{(1)}:
We apply the BV relation to the left hand side.
Since $\mu_k(\gamma_1,\ldots,\gamma_k)$ is divergence-free, the left hand side is
\[
\sum \left(\div \gamma_{i_1} \wedge \mu_k(\gamma_{i_2}, \ldots, \gamma_{i_{k+1}}) + \{\gamma_{i_1}, \mu_k(\gamma_{i_2},\ldots, \gamma_{i_{k+1}})\} \right) .
\]
The second terms in the sum cancels with the right hand side of the Jacobi identity.
Thus, it suffices to show that 
\[
\sum \div \gamma_{i_1} \wedge \mu_k(\gamma_{i_2}, \ldots, \gamma_{i_{k+1}}) = 0 .
\]
Notice that this expression only depends on the divergences of the polyvector fields $\gamma_1,\ldots, \gamma_{k+1}$. 
Moreover, it is totally symmetric in the inputs. 
Thus, we can write it as $L(\div \gamma_1,\ldots, \div \gamma_{k+1})$ where
\[
L \colon \Sym^{k+1} \left(\wedge^{2k-2} V \right) \to V
\]
is some ${\rm SL}(2k+1)$-invariant map. 
Here $V$ denotes the defining ${\rm SL}(2k+1)$ representation.
As such $L= 0$ \brian{justify}.

\ul{(2)}: 
The left hand side of the Jacobi identity reads
\begin{equation}\label{eqn:3jacobi2a}
(\div \mu) \mu_k (\gamma_1,\ldots, \gamma_k) + \sum_{i=1}^k \{\div \mu, \gamma_i\} \vee \bigg[\left(\Omega \vee \gamma_1\right) \cdots \Hat{\partial \left(\Omega \vee \gamma_i\right)} \cdots \partial \left(\Omega \vee \gamma_k\right) \bigg]
\end{equation}
Consider the first term on the right hand side of the Jacobi identity. 
Expanding out, we can write this as
\begin{equation}\label{eqn:3jacobi2b}
\sum_{i=1}^k \{\mu, \div \gamma_i\} \vee \bigg[\left(\Omega \vee \gamma_1\right) \cdots \Hat{\partial \left(\Omega \vee \gamma_i\right)} \cdots \partial \left(\Omega \vee \gamma_k\right) \bigg] + \# (\div \mu) \mu_k(\gamma_1,\ldots, \gamma_k) .
\end{equation}
The final term cancels with the first term of \eqref{eqn:3jacobi2a}. 
The remaining terms on the right hand side of the Jacobi relation read
\[
\sum_{i=1}^k \partial \{\mu, \gamma_i\} \vee \bigg[\left(\Omega \vee \gamma_1\right) \cdots \Hat{\partial \left(\Omega \vee \gamma_i\right)} \cdots \partial \left(\Omega \vee \gamma_k\right) \bigg] .
\]
This cancels with the sum of the second term in \eqref{eqn:3jacobi2a} and the first term in \eqref{eqn:3jacobi2b}.
\end{proof}
\end{document}
